---
title: "Results"
author: Kristoffer Wild
date: "`r Sys.Date()`"
output: 
  word_document:
    reference_docx: template.docx
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, eval = T, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
options(digits = 2)
rm(list=ls())
sessionInfo()
# Packages
pacman::p_load("dplyr", "MASS", "MCMCglmm", "quantreg","lmerTest", "emmeans", "latex2exp", "DHARMa", "tidybayes", "ggeffects", "bayesplot", "rstanarm", "plotrix", "emmeans", "patchwork", "ggExtra", "sjPlot", "kableExtra","flextable", "orchaRd", "ggplot2", "metafor", "broom", "plotrix")
```
# Results
```{r TprefCTmaxResults, echo = FALSE, include = FALSE}
## Tpref raw data
Tpref <- read.csv("~/Dropbox/Lampro_project/Final.Analysis.Data/Tpref_datasheet_2020.csv")  %>% 
  mutate(Incubation_temp = gsub("[AC]-", "", trt),
         Yolk_treat = gsub("-.*", "", trt)) %>% 
  rename(id = "bd_liz_id",
         Tpref = "mean_temp") %>% 
  mutate(Inc_temp = as.character(Incubation_temp))

# summary
Tpref.Range <- Tpref %>% 
  summarise(n = n(),
            min = min(Tpref),
            max = max(Tpref), 
            mean = mean(Tpref),
            se = std.error(Tpref)) %>% 
  round(2)

# CTmax
CT.data.raw <- read.csv("~/Dropbox/Lampro_project/Final.Analysis.Data/CTmax_datasheet_2020.csv") %>%
  mutate(Incubation_temp = gsub("[AC]-", "", trt),
         Yolk_treat = gsub("-.*", "", trt)) %>% 
  rename(id = "bd_liz_id") %>% 
  mutate(Inc_temp = as.character(Incubation_temp))
# summary
CTmax.Range <- CT.data.raw %>% 
  summarise(min = min(CTmax),
            max = max(CTmax), 
            mean = mean(CTmax),
            se = std.error(CTmax)) %>% 
  round(2)
```
*(a)Incubation temperature and resource allocation consequences on thermal preference and critical thermal maximum*
<p>Hatchling *Lampropholis delicata* (n=40) were measured for thermal preference (T$_{pref}$) and critical thermal maximum,with (n=10) per resource treatment (yolk removal and control) by incubation temperature (23 & 28°C). Mean T$_{pref}$ was `r Tpref.Range[1,4]`$^\circ$C ±SE`r Tpref.Range[1,5]`and ranged from `r Tpref.Range[1,2]`–`r Tpref.Range[1,3]`$^\circ$C. Mean CT$_{max}$ was `r CTmax.Range[1,3]`$^\circ$C ±SE`r CTmax.Range[1,4]` and ranged from `r CTmax.Range[1,1]`–`r CTmax.Range[1,2]`$^\circ$C. We did not detect any effect of incubation temperature, yolk treatment, sex, or body mass on T$_{pref}$ or CT$_{max}$ (Figure 1A|B; Table 1).<p>
```{r MetaAnalysisResults, echo = FALSE, include = FALSE}
# overall mod
model_all_rand <- readRDS("~/Dropbox/Lampro_project/Final.Models/Meta_analysis_models/Meta_mods_accl_ratio/meta.acc.phylo.allrand.rds")
I2_all <- as.data.frame(round(i2_ml(model_all_rand),digits = 2))
I2_all_predict <- as.data.frame(predict(model_all_rand))
I2_all_predict <- round(I2_all_predict, digits = 2)
# spp mod
spp_mod <- readRDS("~/Dropbox/Lampro_project/Final.Models/Meta_analysis_models/Meta_mods_accl_ratio/meta.acc.no.phylo.rds")
I2_spp <- as.data.frame(round(i2_ml(spp_mod),digits = 2))
mod_bias <- readRDS("~/Dropbox/Lampro_project/Final.Models/Meta_analysis_models/Meta_mods_accl_ratio/mod_bias.rds")
mod_bias_b <- as.data.frame(mod_bias$b)
mod_bias_lb <-as.data.frame(mod_bias$ci.lb)
mod_bias_ub <-as.data.frame(mod_bias$ci.ub)
mod_bias_pvalue <- as.data.frame(mod_bias$pval)
```
*(b)	Meta-analysis of early thermal effects on thermal physiology in reptiles*
<p>Across reptiles, developmental temperatures did not influence thermal traits (T_pref or CT_max), but heterogeneity was high (ARR =`r I2_all_predict[5,1]`-, 95% CI:`r I2_all_predict[1,3]`-`r I2_all_predict[1,4]` ; $I^2_{Total}$ = `r I2_all[1,1]`%, Prediction Interval:`r I2_all_predict[1,5]`-`r I2_all_predict[1,6]`; Fig. 2A, n = 69 effects from 13 species). Species effects ($I^2_{Species}$ = `r I2_spp[3,1]`%) drove most of the heterogeneity in ARR, but thermal traits were not influenced by life stage, climatic zone or major taxonomic group (i.e., snakes, turtles, lizards) (Fig. 2B|C). However, there was a significant increase in thermal traits in snakes, but this was driven by a single species (*Nerodia sipdedon*) (Fig 2D). We found no evidence for publication biases ($\beta$=`r mod_bias_b[2,1]`, 95%CI=`r mod_bias_lb[2,1]`-`r mod_bias_ub[2,1]`, *p=`r mod_bias_pvalue[2,1]`*; Fig S4; for further details see electronic supplementary materials).
<p>

\newpage
# Tables & Figures
Table 1. Model outputs coefficients for testing wither sex, body mass, incubation temperature, resource, or the interaction between resource and temperature had an effect on T$_{Pref}$ or CT$_{Max}$ in hatchling *Lampropholis delicata*. Est. value describes the estimated coefficient value and 95% CI describes the lower and upper bound of the 95% credible interval for each coefficient value. Intercept is the estimated mean of each thermal trait from the null model. 
```{r Table1,echo= FALSE}
################ Tpref
# Tabulate the model coefficients
# M5 accounts for all main effects but interaction (M6 - which is NS)
Tpref_m5_table <- readRDS(file = "~/Dropbox/Lampro_project/Final.Models/Tpref_models/Tpref.m5.rds") %>%
  tidy(conf.int = TRUE) 
Tpref_m5_table[2,1] <- "Body Mass"
Tpref_m5_table[3,1] <- "Sex"
Tpref_m5_table[4,1] <- "Incubation Temperature"
Tpref_m5_table[5,1] <- "Resource"

# M6 = Resource*Temp interaction (M6)
Tpref_m6_table <- readRDS(file = "~/Dropbox/Lampro_project/Final.Models/Tpref_models/Tpref.m6.rds") %>% 
  tidy(conf.int=TRUE) %>% 
  filter(term == "temp28:treatC") 
Tpref_m6_table[1,1] <- "Incubation Temperature*Resource"

# arranging Tpref Table
Tpref.Tbl.comb <- rbind(Tpref_m5_table, Tpref_m6_table) %>% 
  dplyr::select(-c("std.error","statistic")) %>% 
  mutate("Thermal Index" = "Tpref")
Tpref.Tbl.1 <- Tpref.Tbl.comb[,c(6,1,2,4,5,3)]

################ CT MAX
# Tabulate the model coefficients 
# M5 accounts for all main effects but interaction (M6 - which is NS)
# m5 = Resource
CTmax_m5_table <- readRDS(file = "~/Dropbox/Lampro_project/Final.Models/CTmax_models/CT.Max.m5.rds") %>% 
  tidy(conf.int = TRUE) 
CTmax_m5_table[2,1] <- "Body Mass"
CTmax_m5_table[3,1] <- "Sex"
CTmax_m5_table[4,1] <- "Incubation Temperature"
CTmax_m5_table[5,1] <- "Resource"

# m6 = Resource*Temp interaction
CTmax_m6_table <- readRDS(file = "~/Dropbox/Lampro_project/Final.Models/CTmax_models/CT.Max.m6.rds") %>%
  tidy(conf.int = TRUE) %>% 
  filter(term == "temp28:treatC") 
CTmax_m6_table[1,1] <- "Incubation Temperature*Resource"

# arranging CTmax Table
CTmax.Tbl.comb <- rbind(CTmax_m5_table, CTmax_m6_table) %>% 
  dplyr::select(-c("std.error","statistic")) %>% 
  mutate("Thermal Index" = "CTmax")
CTmax.Tbl.1 <- CTmax.Tbl.comb[,c(6,1,2,4,5,3)]

############# Final Table 1
Tbl.1 <- as.data.frame(rbind(Tpref.Tbl.1, CTmax.Tbl.1)) %>% 
  rename(Covariate = term,
         Estimate = estimate,
         "l-95% CI" = conf.low,
         "u-95% CI" = conf.high,
         "p value" = p.value) %>% 
  mutate_if(is.numeric, round, 2)
Tbl.1.Final <- flextable(Tbl.1) %>% 
  italic(i = 1:12, j = 1, italic = TRUE) %>% 
  bold(i = 1, j = 2:6, bold = TRUE, part = "body") %>% 
  bold(i = 7, j = 2:6, bold = TRUE, part = "body") %>% 
  hline(i=6, j = 1:6, part="body") %>% 
  merge_v(j = "Thermal Index") %>%  
  autofit(part = "all") %>% 
  align(align ="center", part = "all") %>% 
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.1.Final)
```

\newpage
```{r Fig1AB,echo= FALSE}
# Figure 1 - code for figure can be found in Thermal_gradient.R script
knitr::include_graphics("~/Dropbox/Lampro_project/Final.Figures/Figure1.pdf")
```
Figure 1. Thermal indices across different incubation temperatures and resource treatments for hatchling *Lampropholis delicata* (n=10 per temperature and treatment). (A) Thermal preference (T$_{pref}$) in lizards incubated at 23 & 28°C for each resource treatment (yolk ablation & control). (B) Critical thermal maximum (CT$_{max}$) in lizards incubated at 23 & 28°C for each resource treatment. Bars above plots indicate pairwise comparisons of thermal indices between treatment temperature and the interaction between treatment temperature and resource treatment. 

\newpage
```{r Fig2ABCD,echo= FALSE}
# Figure 2 - - code for figure can be found in meta-analysis.R script s
knitr::include_graphics("~/Dropbox/Lampro_project/Final.Figures/Figure2.pdf")
```
Figure 2. Magnitude of the effect on developmental temperature on thermal indices (T$_{pref}$ & CT$_{max}$) in reptiles (A) with respect to age class (B), climatic zone  (C), and taxon (D). Mean meta-analytic estimates (circles) with their 95% confidence intervals (thicker error bars) and prediction intervals (thinner error bars). Individual data points (colored circles) from each study from meta-analysis are scaled by precision (inverse of standard error) and k is the number of effect sizes with number of species in brackets. ARR is acclimation response ratio. Graphs were constructed using the orchaRd package (Nakagawa et al., 2021; version 2.0).

\newpage
# Supplementary Tables 
```{r FigS1,echo= FALSE}
# figure of lizard in tube
knitr::include_graphics("~/Dropbox/Lampro_project/Final.Figures/FigureS1.pdf")
```
Figure S1.Methods for collecting Tpref in Lampropholis delicata. Lizards were placed in Falcon tubes in a temperature-controlled bath. To obtain the most accurate Tb for skinks, temperature was monitored with a thermocouple probe secured within Falcon tube and an additional thermal couple that was placed in the bath. Water temperature was increased to 38◦C at a rate of 1◦C/min intervals. Every 1min tubes were rotated to check righting reflex of skinks. CTmax was defined as the temperature at which an individual lost their righting reflex.

\newpage
```{r FigS2,echo= FALSE}
# figure of Decision tree
knitr::include_graphics("~/Dropbox/Lampro_project/Final.Figures/FigureS2.pdf")
```
Figure S2. Figure S2. Decision tree showing the eligibility criteria used to assess full-text articles. 

\newpage
```{r FigS3,echo= FALSE}
# PRISMA statemen
knitr::include_graphics("~/Dropbox/Lampro_project/Final.Figures/FigureS3.pdf")
```
Figure S3. PRISMA statement illustrating the systematic literature search and record screening process.

\newpage
```{r FigS4,echo= FALSE}
# Figure S4 - code for figure can be found in meta-analysis.R script
knitr::include_graphics("~/Dropbox/Lampro_project/Final.Figures/FigureS4.pdf")
```
Figure S4. Funnel plot of the meta-analytic residuals against precision (1/SE). Each point represents a pair-wise temperature comparison. There is no visually detectable asymmetry.

\newpage
Table S3. The magnitude of the effect of developmental temperature on ARR on CTmax and Tpref of reptiles. The number of effect sizes is denoted by k  and n indicates the number of species. Estimates are species mean meta-analytic estimates with their 95% confidence intervals (lowerCL = lower bound & upperCL = upper bound) and prediction intervals (lowerPR = lower bound & upperPR = upper bound). P values indicate if values are significantly different from zero. The conditional r$^{2}$ (0.79) and the marginal r$^{2}$ (0.01). 
```{r TableS3,echo= FALSE}
###### Trait
data <- readRDS(file = "~/Dropbox/Lampro_project/Final.Analysis.Data/Meta_df_rmdfile.rds")
model_trait <- readRDS(file = "~/Dropbox/Lampro_project/Final.Models/Meta_analysis_models/Meta_mods_accl_ratio/meta.acc.trait.rds") 
trait_tbl <- mod_results(model_trait, mod="trait", group="study_ID",  data=data)
trait_tbl <- trait_tbl$mod_table
trait_tbl<- trait_tbl %>% mutate("p value" = "", 
                                 "k" = "",
                                 "n" = "")
# add pvalues
trait_tbl[1,7] <- round(0.8443, digits = 2)
trait_tbl[2,7] <- round(0.5801, digits = 2)
# adding k
trait_tbl[1,8] <- 21
trait_tbl[2,8] <- 61
# adding sample size
trait_tbl[1,9] <- 6
trait_tbl[2,9] <- 15

# marginal and conditional r2
model_trait_r2 <- round(r2_ml(model_trait), digits = 2)

############# Final Table S3
Tbl.S3 <- trait_tbl %>% 
  rename("Thermal metric" = name,
         Estimate = estimate) %>% 
  mutate_if(is.numeric, round, 2)
Tbl.S3 <-  Tbl.S3[,c(1,8,9,2,4,5,6,7)]
Tbl.S3.Final <- flextable(Tbl.S3) %>% 
  italic(i = 1:2, j = 1, italic = TRUE) %>%  
  autofit(part = "all") %>% 
  align(align ="center", part = "all") %>% 
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.S3.Final)
```

\newpage
Table S4. The magnitude of the effect of developmental temperature on ARR when accounting for age class. The number of effect sizes is denoted by k and n indicates the number of species. Estimates are species mean meta-analytic estimates with their 95% confidence intervals (lowerCL = lower bound & upperCL = upper bound) and prediction intervals (lowerPR = lower bound & upperPR = upper bound). P values indicate if values are significantly different from zero. The conditional r$^{2}$ (0.80) and the marginal r$^{2}$ (0.01).
```{r TableS4,echo= FALSE}
###### Trait
data <- readRDS(file = "~/Dropbox/Lampro_project/Final.Analysis.Data/Meta_df_rmdfile.rds")
data$age <- factor(data$age, levels=c("adult", "juvenile", "hatchling"))
model_age <- readRDS(file = "~/Dropbox/Lampro_project/Final.Models/Meta_analysis_models/Meta_mods_accl_ratio/meta.acc.age.rds") 
age_tbl <- mod_results(model_age, mod="age", group="study_ID",  data=data)
age_tbl <- age_tbl$mod_table
age_tbl<- age_tbl %>% mutate("p value" = "", 
                                 "k" = "",
                                 "n" = "")
# add pvalues
age_tbl[1,7] <- round(0.9823, digits = 2)
age_tbl[2,7] <- round(0.9741, digits = 2)
age_tbl[3,7] <-round(0.7236, digits = 2)
# adding k
age_tbl[1,8] <- 10
age_tbl[2,8] <- 28
age_tbl[3,8] <- 23

# adding sample size
age_tbl[1,9] <- 3
age_tbl[2,9] <- 6
age_tbl[3,9] <- 8

# marginal and conditional r2
model_age_r2 <- round(r2_ml(model_age), digits = 2)

############# Final Table S3
Tbl.S4 <- age_tbl %>% 
  rename("Age class" = name,
         Estimate = estimate) %>% 
  mutate_if(is.numeric, round, 2)
Tbl.S4 <-  Tbl.S4[,c(1,8,9,2,4,5,6,7)]
Tbl.S4.Final <- flextable(Tbl.S4) %>% 
  italic(i = 1:3, j = 1, italic = TRUE) %>%  
  autofit(part = "all") %>% 
  align(align ="center", part = "all") %>% 
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.S4.Final)
```

\newpage
Table S5. The magnitude of the effect of developmental temperature on ARR when accounting for the species origin. The number of effect sizes is denoted by k  and n indicates the number of species. Estimates are species mean meta-analytic estimates with their 95% confidence intervals (lowerCL = lower bound & upperCL = upper bound) and prediction intervals (lowerPR = lower bound & upperPR = upper bound). P values indicate if values are significantly different from zero. The conditional r$^{2}$ (0.80) and the marginal r$^{2}$ (0.01).
```{r TableS5,echo= FALSE}
###### Geographic zone
data <- readRDS(file = "~/Dropbox/Lampro_project/Final.Analysis.Data/Meta_df_rmdfile.rds")
model_geo <- readRDS(file = "~/Dropbox/Lampro_project/Final.Models/Meta_analysis_models/Meta_mods_accl_ratio/meta.acc.zone.rds") 
geo_tbl <- mod_results(model_geo, mod="zone", group="study_ID",  data=data)
geo_tbl <- geo_tbl$mod_table
geo_tbl<- geo_tbl %>% mutate("p value" = "", 
                                 "k" = "",
                                 "n" = "")
# add pvalues
geo_tbl[1,7] <- round(0.7416, digits = 2)
geo_tbl[2,7] <- round(0.9447, digits = 2)
# adding k
geo_tbl[1,8] <- 55
geo_tbl[2,8] <- 6

# adding sample size
geo_tbl[1,9] <- 14
geo_tbl[2,9] <- 1

# marginal and conditional r2
model_geo_r2 <- round(r2_ml(model_geo), digits = 2)

############# Final Table S3
Tbl.S5 <- geo_tbl %>% 
  rename("Geographic zone" = name,
         Estimate = estimate) %>% 
  mutate_if(is.numeric, round, 2)
Tbl.S5 <-  Tbl.S5[,c(1,8,9,2,4,5,6,7)]
Tbl.S5.Final <- flextable(Tbl.S5) %>% 
  italic(i = 1:2, j = 1, italic = TRUE) %>%  
  autofit(part = "all") %>% 
  align(align ="center", part = "all") %>% 
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.S5.Final)
```

\newpage
Table S6. The magnitude of the effect of developmental temperature on ARR when accounting for reptile taxa. The number of effect sizes is denoted by k and n indicates the number of species. Estimates are species mean meta-analytic estimates with their 95% confidence intervals (lowerCL = lower bound & upperCL = upper bound) and prediction intervals (lowerPR = lower bound & upperPR = upper bound). P values indicate if values are significantly different from zero. The conditional r$^{2}$ (0.80) and the marginal r$^{2}$ (0.38).
```{r TableS6,echo= FALSE}
###### Trait
data <- readRDS(file = "~/Dropbox/Lampro_project/Final.Analysis.Data/Meta_df_rmdfile.rds")
model_taxa <- readRDS(file = "~/Dropbox/Lampro_project/Final.Models/Meta_analysis_models/Meta_mods_accl_ratio/meta.acc.taxon.rds") 
taxa_tbl <- mod_results(model_taxa, mod="class", group="study_ID",  data=data)
taxa_tbl <- taxa_tbl$mod_table
taxa_tbl<- taxa_tbl %>% mutate("p value" = "", 
                                 "k" = "",
                                 "n" = "")
# add pvalues
taxa_tbl[1,7] <- round(0.3720, digits = 2)
taxa_tbl[2,7] <- round(0.0110, digits = 2)
taxa_tbl[3,7] <-round(0.6348, digits = 2)
taxa_tbl[4,7] <-round(0.4377, digits = 2)
# adding k
taxa_tbl[1,8] <- 41
taxa_tbl[2,8] <- 7
taxa_tbl[3,8] <- 2
taxa_tbl[4,8] <- 11

# adding sample size
taxa_tbl[1,9] <- 10
taxa_tbl[2,9] <- 2
taxa_tbl[3,9] <- 1
taxa_tbl[4,9] <- 2

# marginal and conditional r2
model_taxa_r2 <- round(r2_ml(model_taxa), digits = 2)

############# Final Table S3
Tbl.S6 <- taxa_tbl %>% 
  rename("Taxa" = name,
         Estimate = estimate) %>% 
  mutate_if(is.numeric, round, 2)
Tbl.S6 <-  Tbl.S6[,c(1,8,9,2,4,5,6,7)]
Tbl.S6.Final <- flextable(Tbl.S6) %>% 
  italic(i = 1:4, j = 1, italic = TRUE) %>%  
  autofit(part = "all") %>% 
  align(align ="center", part = "all") %>% 
  font(part = "all", fontname = "Times New Roman") %>% 
  fix_border_issues() 
knitr::knit_print(Tbl.S6.Final)